|

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.Rmd
adjust the introduction based on more information on the writings

Abundance of literature describe appropriate diagnostic methods for linear regression: @draper1998applied, @montgomery1982introduction, @belsley_regression_1980, @cook_applied_1999 and @cook1982residuals. The diligent reader of these sage writings will also notice sentences that express sentiments like *based on their experience, statistical tests are not widely used in regression diagnostics since the same or even larger amount of information can be provided by diagnostic plots than the corresponding tests in most empirical studies.* A common guidance by experts is that optimal method for diagnosing model fits is by plotting the data.

The persistence of this advice to check the plots is curious, and investigating why this might be common advice is the subject of this paper. The paper is structured as follows. The next background section describes the types of departures that one expects to detect, and outlines a formal statistical process for reading residual plots, called visual inference. Section \ref{experimental-design} details the experimental design to compare the decision made by formal hypothesis testing, and how humans would read diagnostic plots. The results are reported in Section \ref{results}. We finish with a discussion on future work, in particular how the responsibility for residual plot reading might be relieved.

@@

### Lineup protocol

@@

### Sampling from the null distribution

### $p$-values of a visual test

@@

To investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics, an experiment is conducted in three data collection periods. The two types of departures, non-linearity and heteroskedasticity, are primarily collected during data collection periods I and II. The data collection period III was designed primarily to measure human responses to null lineups so that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Additional lineups for both non-linearity and heteroskedasticity, using uniform $X$ distribution, were included so that the participants were evaluating some lineups with signal also. It would be too frustrating for participants to only be assigned lineups with all null plots. Overall, we collected `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three data collection periods.

@@

## Methodology

### Power of a visual test

>>>>

Abundance of literature describe appropriate diagnostic methods for linear regression: @draper1998applied, @montgomery1982introduction, @belsley_regression_1980, @cook_applied_1999 and @cook1982residuals. All of these writings consider plotting of residuals to be a standard technique that should be examined routinely in all regression modelling problems. In addition, @draper1998applied and @belsley_regression_1980 believe that residual plots are usually very revealing when the assumptions are violated. @cook_applied_1999 thinks formal tests and graphical procedures are complementary and both have a place in residual analysis, but they focus on graphical methods rather than on formal testing, as they are easier to use. @montgomery1982introduction even suggests that residual plots are more informative in most practical situations than corresponding formal tests, and statistical tests on regression model residuals are not widely used based on their experience.

A common guidance by experts is that optimal method for diagnosing model fits is by plotting the data. The persistence of this advice to check the plots is curious, and investigating why this might be common advice is the subject of this paper. The paper is structured as follows. The next background section describes the types of departures that one expects to detect, and outlines a formal statistical process for reading residual plots, called visual inference. Section \ref{experimental-design} details the experimental design to compare the decision made by formal hypothesis testing, and how humans would read diagnostic plots. The results are reported in Section \ref{results}. We finish with a discussion on future work, in particular how the responsibility for residual plot reading might be relieved.

@@

@@

# Caluculation of p-value, effect size and power

Visual inference is

To be able to properly compare conventional tests to visual tests, we need to define the effect size of the residual departure, the power of the tests under a certain level of effect size,

@@

To investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics, an experiment is conducted in three data collection periods. Two types of departures, non-linearity and heteroskedasticity, are primarily collected during data collection periods I and II. The data collection period III was designed primarily to measure human responses to null lineups so that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Additional lineups for both non-linearity and heteroskedasticity, using uniform $X$ distribution, were included so that the participants were evaluating some lineups with signal also. It would be too frustrating for participants to only be assigned lineups with all null plots. Overall, we collected `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three data collection periods.

@@
